Verifying Demonstrations

### 2017-08-04 properties.tex
Merges authenticity with verification
Makes the authenticity requirements part of eligibility verification.

\mode*
\section[Verification and privacy]{Authenticity, verification and privacy}

@@

\subsection{Data authenticity}
\label{DataAuthenticity}

The problem of authentically associating data with a physical event is 
difficult.
We can essentially divide it into the following requirements:
\begin{frame}
\begin{requirements}[A]
  \item\label{CreatedAfterStart} Prove that the data was created after the 
    start of the event.
  \item\label{CreatedBeforeEnd} Prove that the data was created before the end 
    of the event.
  \item\label{SpatiallyRelated} Prove that the data is spatially related to the 
    physical location of the event.
\end{requirements} %TODO: A4 accurate/not fabricated?

\mode<presentation>{
\begin{idea}
  \begin{itemize}
    \item There is a mechanism that provides A\ref{CreatedAfterStart} and 
      A\ref{CreatedBeforeEnd}: a blockchain.

    \item There are also other structures, e.g.\ a directed 
      graph~\cite{BlockchainFreeCryptocurrencies}.

    \item Add a consensus protocol and Eve must subvert a majority to change 
      the outcome.

    \item A\ref{SpatiallyRelated} can be provided by \iacf{LP}.
  \end{itemize}
\end{idea}
}
\end{frame}
\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{partial 
  order}\footnote{%
  A relation \(\preceq\) which is reflexive, antisymmetric and transitive.
}.
If some objects in the set relate to known points in time, then the partial 
order allows to relate the data to the time of the event.
This allows us to \emph{authenticate the data temporally}.
\Cref{SpatiallyRelated} binds the data spatially to the location, which allows 
us to \emph{authenticate the data spatially}.

@@

In general, protesting is very similar to voting: both are many individuals 
expressing their opinion.
Hence we desire to have similar properties of verification and privacy for 
participation in a protest as there is for voting.
In the context of (electronic) voting protocols, there are three requirements 
for verification~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{frame}
\begin{requirements}[V]
\item\label{EligibilityVerif} Eligibility: anyone can verify that each vote 
  cast is legitimate.
\item\label{UniversalVerif} Universal verifiability: anyone can verify that the 
  result is according to the cast votes.
\item\label{IndividualVerif} Individual verifiability: every voter can verify 
  that their vote is included in the result.
\end{requirements}
\end{frame}
We can translate these to the case of participation in a demonstration, then 
each vote would be replaced by a proof of participation.
To have any verifiability, we need the storage (e.g.\ blockchain) to be 
immutable --- i.e.\ it prevents malicious changes.

@@

If the proofs are stored publicly, then an individual can check that their 
proof has been included there.
Thus \cref{IndividualVerif} is fulfilled.

@@

\Cref{EligibilityVerif} would in this case mean that anyone can verify that 
each participation proof belongs to a unique individual, i.e.\ to prevent Sybil 
attacks.
They must also be able to detect if the proof is reused from a previous protest 
(i.e.\ related to \cref{CreatedAfterStart,CreatedBeforeEnd}).

@@

If the blockchain is public, then anyone can download all the proofs, verify 
them (eligibility) and count them.
Thus anyone can verify the result, which fulfils \cref{UniversalVerif}.

>>>>

\mode*
\section{Verification and privacy}

@@

@@

In general, protesting is very similar to voting: both are many individuals 
expressing their opinion.
Hence we desire to have similar properties of verification and privacy for 
participation in a protest as there is for voting.
In the context of (electronic) voting protocols, there are three requirements 
for verification~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{frame}
\begin{requirements}[V]
\item\label{EligibilityVerif} Eligibility: anyone can verify that each vote 
  cast is legitimate.
\item\label{UniversalVerif} Universal verifiability: anyone can verify that the 
  result is according to the cast votes.
\item\label{IndividualVerif} Individual verifiability: every voter can verify 
  that their vote is included in the result.
\end{requirements}
\end{frame}
We can translate these to the case of participation in a demonstration, then 
each vote would be replaced by a proof of participation.

@@

If the proofs are stored publicly, then an individual can check that their 
proof has been included there.
Thus \cref{IndividualVerif} is fulfilled.
To have any verifiability, we need the storage (e.g.\ blockchain) to be 
immutable --- i.e.\ it prevents malicious changes.

@@

\Cref{EligibilityVerif} would in this case mean that anyone can verify that 
each participation proof belongs to a unique individual, i.e.\ to prevent Sybil 
attacks.
They must also be able to verify that each proof is indeed related to the 
event.
We must associate the proof to the event both spatially (the correct location) 
and temporally (it is related to the time-interval of the event).
We can essentially divide it into the following requirements:
\begin{frame}
\begin{requirements}[\ref*{EligibilityVerif}.]
  \item\label{UniqueIndividual} Prove that the data is unique for an 
    individual.
  \item\label{CreatedAfterStart} Prove that the data was created after the 
    start of the event.
  \item\label{CreatedBeforeEnd} Prove that the data was created before the end 
    of the event.
  \item\label{SpatiallyRelated} Prove that the data is spatially related to the 
    physical location of the event.
\end{requirements}
\end{frame}

\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{partial 
  order}\footnote{%
  A relation \(\preceq\) which is reflexive, antisymmetric and transitive.
}.
If some objects in the set relate to known points in time, then the partial 
order allows to relate the data to the time of the event.
This allows us to \emph{verify the data temporally}.
\Cref{SpatiallyRelated} binds the data spatially to the location, which allows 
us to \emph{verify the data spatially}.

@@

If the storage is public, then anyone can download all the proofs, verify them 
and count them.
Thus anyone can verify the result, which fulfils \cref{UniversalVerif}.
